\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-06-01 doc/USER_MANUAL/05_running_the_solver.tex
Add new option for external source time function: modification of Par_files and add some lines in manual

>>>>

 In addition to inbuild source time function, the solver can also use an external source time function defined by the user. This option can be  
activated by setting   \texttt{EXTERNAL\_SOURCE\_FILE} to true in \texttt{Par\_File} and by adding the name of the file
containing the source time function at the end of \texttt{FORCESOLUTION} or \texttt{CMTSOLUTION} files. The source time function file must 
contain 2 columns with the current time and the amplitude of the soure function. The time step must be the same as used for the 
simulation. Note  when the  \texttt{EXTERNAL\_SOURCE\_FILE} is set to false then the line with the external source time function file must not appear in 
the files  \texttt{FORCESOLUTION} and \texttt{CMTSOLUTION} otherwise the solver will exit with an error.
